Finiteness and Cardinality in Homotopy Type Theory

### 2020-01-13 paper.tex
dependent function types for cardinal finiteness

\input{preamble}
\title{Finiteness and Cardinality in Homotopy Type Theory}
\author{Donnacha Oisín Kidney}
\authorrunning{D. O. Kidney}
\institute{University College Cork \and
  \email{o.kidney@cs.ucc.ie}}
\begin{document}
\maketitle
\begin{abstract}
  We explore five notions of finiteness in Homotopy Type Theory \cite{hottbook}.
  We will classify these notions, and prove their closure properties,
  culminating in a proof that decidable Kuratowski-finite sets
  \cite{kuratowskiNotionEnsembleFini1920} form a topos.

@@

  We formalise our work in Cubical Agda
  \cite{vezzosiCubicalAgdaDependently2019}, and we implement a library for proof
  search (including combinators for level-polymorphic fully generic currying),
  and demonstrate how it can be used to both prove properties and synthesise
  full functions given desired properties.
\end{abstract}
\section{Introduction}
\subsection{Strong Finiteness Predicates}
\input{figures/finite-classification}
We will first explore the ``strong'' notions of finiteness (i.e. those at least
as strong as Kuratowski finiteness \cite{kuratowskiNotionEnsembleFini1920}),
with a special focus on cardinal finiteness (section~\ref{cardinal}), and
manifest enumerability (section~\ref{manifest-enumerability}), which is new, to
our knowledge.

>>>>

\input{preamble}
\title{Finiteness and Cardinality in Homotopy Type Theory}
\author{Donnacha Oisín Kidney}
\authorrunning{D. O. Kidney}
\institute{University College Cork \and
  \email{o.kidney@cs.ucc.ie}}
\begin{document}
\maketitle
\begin{abstract}
  We study finiteness in Homotopy Type Theory, classifying five fundamentally
  different finiteness predicates and proving formally the relationship between
  them.
  We also prove the closure properties of each predicate, which includes a proof
  that decidable Kuratowski finite sets form a topos.

@@

  We formalise our work in Cubical Agda, and we implement a library for proof
  search (including combinators for level-polymorphic fully generic currying),
  and demonstrate how it can be used to both prove properties and synthesise
  full functions given desired properties.
\end{abstract}
\section{Introduction}
\subsection{Strong Finiteness Predicates}
\input{figures/finite-classification}
We will first explore the ``strong'' notions of finiteness (i.e. those at least
as strong as Kuratowski finiteness \cite{kuratowskiNotionEnsembleFini1920}),
with a special focus on cardinal finiteness (section~\ref{cardinal}), and
manifest enumerability (section~\ref{manifest-enumerability}), which is new, to
our knowledge.
